si: code and prose exploring Spatial Interaction models

### 2024-08-04 README.qmd
Document new data

```{r}
#| echo: false
#| eval: false
# Add actions:
usethis::use_github_action("check-standard")
# Add pkgdown action:
usethis::use_github_action("pkgdown")
```

>>>>

```{r}
#| echo: false
#| eval: false
# Add actions:
usethis::use_github_action("check-standard")
# Add pkgdown action:
usethis::use_github_action("pkgdown")
usethis::use_data_raw("si_oa_wpz")
```
